Probability of causal contact between interstellar civilizations through MonteCarlo simulations

### 2019-08-20 manuscript.tex
figura de primer contacto con make up

\begin{figure*}
   \centering
   \includegraphics[width=\textwidth]{Messages_01.pdf}
   \caption{Schematic representation of the possible cases in which a
   ceti A can be in causal contact with a ceti B which appears later.
   The duration of the causal contact in one direction depends on
   several factors, mainly $\Delta t_A$, $\Delta t_C$, and $\Delta X$.}
   \label{F_messages}
\end{figure*}

@@

In this section we analyze the distribution of the waiting times for
a first contact.
%
Such distribution can be considered to compute the probability for a
random CETI to carry out a SETI project and spend a given time until
the first contact is made.
%
Reaching a first contact within the first $t_1$ years of a SETI project,
requires assuming that the methods are correct and the hypotheses of
the experiment fullfil.
%
This values can be considered as upper limits, since the efficiency of
a SETI initiative could be smaller than the ideal.
%
Also, a civilization could consider itself as "awakened" before it
discovers the right technology to perform a communication.

@@

... but not in the case of different values of $\tau_s$.

%    \caption{Fraction of the CETIs that have made at least one contact  
%   as a funtion of the elapsed time since the awakening, given that they make at least one contact on their lifetime.
%   %
%   From a frequentist approach, this fraction is the estimation of the
%   probability}

@@

\hline
\end{tabular}
\caption{Selected models to analize the behevior of simulation outputs
   and their dependence on simulation outputs and their dependence on
   simulation parameters..}
\label{T_SelectedModels}
\end{table*}

@@

\begin{figure}
   \centering
   \includegraphics[width=0.5\textwidth]{radial.png}
   \caption{Fraction of CETIs making cero, one, two or three contacts as a function of
   galactocentric distance.}
   \label{F_radial}
\end{figure}

@@

\begin{figure*}
   \centering
   \includegraphics[width=0.5\textwidth]{Figure_taua.png}%
   \includegraphics[width=0.5\textwidth]{Figure_taus.png}
   %
   \caption{Histograms of the mean waiting times for the first contact, for
   several models.
   %
   Left panel shows the histograms for several values of $\tau_a$, and
   $\tau_s$ in the range 17000-24000 yr.
   %
   Right panel shows the histograms for several values of $\tau_s$, and
   $\tau_a$ in the range 68000-100000 yr.
   %
   The shape of the histograms does not change when $\tau_a$ is
   modified, but significantly changes when $\tau_s$ is modified.
   }
   \label{F_waiting}
\end{figure*}

>>>>

\begin{figure*}
   \centering
   \includegraphics[width=0.8\textwidth]{Messages_01.pdf}
   \caption{Schematic representation of the possible cases in which a
   ceti A can be in causal contact with a ceti B which appears later.
   The duration of the causal contact in one direction depends on
   several factors, mainly $\Delta t_A$, $\Delta t_C$, and $\Delta X$.}
   \label{F_messages}
\end{figure*}

@@

In this section we analyze the distribution of the waiting times for
a first contact.
%
%Such distribution can be considered to compute the probability of
%reaching a first contact within the first XX years of a SETI project,
%assuming the methods are correct and the hypotheses of the experiment.
Such distribution can be considered to compute the probability for a
random CETI to carry out a SETI project and spend a given time until
the first contact is made.

@@

@@

\hline
\end{tabular}
\caption{Selected models to analize the behevior of simulation outputs
   and their dependence on simulation outputs and their dependence on
   simulation parameters.}
\label{T_SelectedModels}
\end{table*}

@@

@@

\begin{figure}
   \centering
   %\includegraphics[width=0.5\textwidth]{Figure_taua.png}%
   %\includegraphics[width=0.5\textwidth]{Figure_taus.png}
   \includegraphics[width=0.5\textwidth]{waiting_s+a_dif_ylog.pdf}
   %
   \caption{Histograms of the mean waiting times for the first contact, for
   several models.
   %
   Left panel shows the histograms for several values of $\tau_a$, and
   $\tau_s$ in the range 17000-24000 yr.
   %
   Right panel shows the histograms for several values of $\tau_s$, and
   $\tau_a$ in the range 68000-100000 yr.
   %
   The shape of the histograms does not change when $\tau_a$ is
   modified, but significantly changes when $\tau_s$ is modified.
   }
   \label{F_waiting}
\end{figure}

\begin{figure}
   \centering
   \includegraphics[width=0.5\textwidth]{radial.png}
   \caption{Fraction of CETIs making cero, one, two or three contacts as a function of
   galactocentric distance.}
   \label{F_res_5}
\end{figure}
